### 2021-07-31 doc/src/IMSIC.tex
Clarify delay and ordering of writes to an interrupt file's memory region

Stores by a hart to an interrupt file's memory-mapped registers
may be arbitrarily delayed before appearing in the appropriate
interrupt-pending bits.
Whether, after accounting for these delays, such writes always
remain in the same order they were executed by the hart is
implementation-defined (or possibly platform-defined).

\begin{commentary}
It is an open question whether stores from a hart to an interrupt file
should, in all systems, be required to remain always in the same order
as executed by the hart.
\end{commentary}

>>>>

When not ignored, writes to an interrupt file's memory region are
guaranteed to be reflected in the interrupt file eventually, but not
necessarily immediately.
For a single interrupt file, the effects of multiple writes (stores) to
its memory region, though arbitrarily delayed, always occur in the same
order as the \textit{global memory order} of the stores as defined by
the {\RISCV} Unprivileged ISA.

\begin{commentary}
In most circumstances, any delay between the completion of a write to
an interrupt file's memory region and the effect of the write on the
interrupt file is indistinguishable from other delays in the memory
system.
However, if a hart writes to a \z{seteipnum\_le} or \z{seteipnum\_be}
register of its own IMSIC, then a delay between the completion of the
store instruction and the consequent setting of an interrupt-pending
bit in the interrupt file may be visible to the hart.
\end{commentary}
